\section{External Interface Requirement}
\subsection{User Interfaces}
\par
\par
\par
\par
\par
\subsection{Hardware Interfaces}
\subsection{Software Interfaces}
\subsection{Communication Interfaces}

\section{Scenarios}
    \subsection{Scenario 1}
    Nike is a worldwide brand of sportswear mainly focused on shoes. The company wants to introduce a new model of shoes addressed to younger people that live in metropolis. Carl, the research manager of the company, wants to understand the habits concerning walking of the young people who are the target for this new model of shoes.
    Fortunately, he has just read on a famous daily newspaper about a new service called Data4Help, which collects data of a huge amount of people all around the world. After Carl has been registered to the service, he can make a request for data by filling the apposite form. Data4Help offers the possibility to customize a request by selecting a range for some categories. He selects as parameters of the request "people living in city with more than one million inhabitants" and "people aged between 15 and 25 years".
    TrackMe approves the request since it refers to more than 1000 people and it sends to Carl all the demanded data.
    Now Carl can carry on his project since he know the target's habits.

    \subsection{Scenario 2}
    Anna is really worried since her mother's latest accident. Her mother is elderly and from now on, also due to the broken foot, has to rest to bed for some period. Martha, a friend of Anna, recommends her a new system of monitoring health status focused on elderly people. After a short research on the net, she downloads AutomatedSOS on her mobile phone and buys a specific electronic device compatible with the app to be supplied to her mother. 
    Anna registers her mother to the service by filling the gaps (user name, password and Fiscal Code) in the interface provided by AutomatedSOS.
    After the confirmation message, it starts to acquire health parameters (such as position, heart rate, skin temperature, blood glucose level and so on) and it sends them to AutomatedSOS every 2 seconds.
    Anna can breathe a sigh of relief: whenever her mother will be in danger, AutomatedSOS will detect it by comparing the parameters provided by the electronic device with specific thresholds. 
    If an emergency occurs, AutomatedSOS will send a request to the Operations Center of the NHS for an ambulance within 5 seconds. The request will include the parameters and also her position, so that the ambulance can estimate the alert level, it can reach Anna’s mother and can provide her first aid.
    Hope it will never occur!

    \subsection{Scenario 3}
    Bianca is a very caring for her son Mark, a 15 years old teenager very lively.
    Mark’s passion is the bike and, unfortunately, he has no friends with whom he could share this sport. At least twice a week Mark, after school, takes a bike ride with his mountain-bike both for the roads and for the wood.
    He is always alone while he is riding so Bianca is worried about Mark safeness.
    Bianca’s hair stylist tell her about a system that monitor real-time position of its users.
    She obliges Mark to download and register to Data4Help application on his smart phone and, meanwhile, also Bianca does it.
    After the login, Bianca makes a request for Mark position by inserting in the apposite form his Fiscal Code. She also subscribes to receive the latest updated position as soon it is available. Mark has only to accept the request of Bianca by pressing the specific button in the Data4Help interface and doing so, he can riding careless of his mother...she always knows his position and she is more quiet. At most every 2 second GPS on Mark’s smart phone collects and sends the latest position to Data4Help system. Once the system receives a new position, it forwards it within 2 seconds to Bianca’s smart-phone. Bianca now can find Mark’s actual position by looking it into the Data4Help interface. 
    Well done!
    
    \subsection{Scenario 4}
    Clara's life is a bit difficult since she was diagnosed with diabetes 5 years ago.
    Up to now she used the traditional method consisting of a blood injection three times a day, every day, to monitor her glucose level.
    During her last periodical check, the doctor told her about a new smart-watch for monitoring blood glucose level in a non intrusive way, detecting it through the sweat.
    This smart-watch is equipped with Data4Help, an innovative system able to collect health parameters of the users.
    Clara must simply download Data4Help app and register with her personal information (Name, Surname, Age, Gender, Fiscal Code or SSN).
    Clara life is simpler from now on, she has just to look the parameters on her smart-watch to know in real time her health status.
    Another functionality of Data4Help allows Clara's doctor to monitor in real-time her patient. After registering to Data4Help as a third party, the doctor make a request for individual data inserting Clara's name, surname and Fiscal Code. In order to receive a continuum stream of data, the doctor makes a subscription request to Clara's parameters.
    Clara has to accept these requests through the functionality provided by Data4Help.
    The doctor has all Clara's parameters in real time and can monitor her health status.
    Next check up will be much faster.
    
    \subsection{Scenario 5}
    Tom is an avid smoker from many years and he suffers of respiratory problems. For this reason he often goes to the doctor to monitor his lungs status.
    Tom's last visit showed a critical health status, so his doctor prescribed him to download AutomatedSOS app on his smart-watch.
    Tom must register to AutomatedSOS by inserting his credentials (name, surname, age, gender, Fiscal Code or SSN) in order to be monitored in real-time.
    AutomatedSOS is built on top of Data4Help, a service that acquires position and health parameters of its users and makes them available to third parties.
    Tom's doctor uses Data4Help to monitor his patient's health status by requesting a subscription to his parameters through the apposite function.
    Tom can accept the request using AutomatedSOS app, since it includes all the Data4Help's functionalities.
    One day, while he is on his way to work, he starts not feeling good. AutomatedSOS system detects an anomaly in the parameters and immediately it elaborates data finding out an emergency. 
    Within 5 seconds from the moment that parameters are received, the system sends a request to the OC of the NHS.
    The request includes Tom health parameters and his position so that NHS can estimates the alert level and provide him first aid.
    As soon as the request arrives to the OC, the situation is clear: Tom is having a heart attack. An ambulance is promptly sent to Tom's location and it arrives within 10 minutes from the moment of the illness.
    Few minutes more would have been fatal.
    Great job AutomatedSOS!
    
    \subsection{Scenario 6}
    Oliver is the responsible of a sports center which include also an athletic track.
    At the moment the track is not in the best condition since it was built 10 years ago, when the sports center opened.
    Oliver would like to restore the track but he wants to be sure that his costumers use it frequently and that the average of the training's length is more than 5 km.
    Oliver is already a user of Data4Help and he knows all the functionalities provided by that service. He asks to all the customer of the sports center that use the athletic track to download and register to Data4Help application on their device. If they don't own one, Oliver would provide them with a smart-watch.
    Of course, during the whole training the customers must bring with them a device equipped with Data4Help app and the GPS active.
    Now Oliver has just to make a request to access to data of a group of people. Through the functionality provided by the app, Oliver fills the form by selecting the following criteria: "People that make physic activities from 8 AM to 10 PM" (the opening hours of the sports center) and "People that make physic activities within 1 km far for Elizabeth road, London, UK" (the location of the sports center).
    Unfortunately, only 438 people corresponds to those criteria so that the system denies the request made by Oliver.
    A negative message appears on his smart-phone showing the reason for the forbidden data.
    Oliver has to find a new way to discover if the investment is a good idea.
    Try again, you'll be luckier.
    

\section{Functional Requirements}
Data4Help:  
\begin{enumerate} [label={[G\arabic*]}]
    \item Allow a visitor to become registered user after providing credentials.
        \begin{itemize}
            \item [{[D1]}] Users insert credentials that correspond to their identity.
            \item [{[D2]}] When a new registered user sends his/her credentials to the system, the message will be surely received.
            \item [{[R1]}] The system should provide a registration form offering the following mandatory fields: name, surname, SSN or Fiscal Code.
            \item [{[R2]}] The system must guarantee that the credentials are unique.
        \end{itemize}
        
    \item Monitor the location of users through electronic devices.
        \begin{itemize}
            \item [{[D3]}] The communication channel doesn't corrupt the data sent by the user's device to the system and vice versa.
            \item [{[D4]}] The electronic device on which the system is installed is equipped with the GPS sensor.
            \item [{[D6]}] The  system  retrieves  the  data  from  the  sensors through the interfaces available on the electronic device.
            \item [{[D7]}] Position information provided by GPS is sufficiently accurate.
            \item [{[R3]}] The system must acquire real-time users' positions from the GPS installed on the user's device.
            \item [{[R4]}] The system must collect users' data in specific databases.
        \end{itemize}
        
    \item Monitor the health status of users through electronic devices.
        \begin{itemize}
            \item [{[D3]}] The communication channel doesn't corrupt the data sent by the user's device to the system and vice versa.
            \item [{[D5]}] The electronic device on which the system is installed is equipped with the sensors related to the parameters tracked by Data4Help.
            \item [{[D6]}] The  system  retrieves  the  data  from  the  sensors  through  the  interfaces available on the electronic device.
            \item [{[D8]}] The sensors related to the health status collect the data with a reasonable precision.
            \item [{[R5]}] The system must acquire real-time users' health parameters from the sensors installed on the user's device.
            \item [{[R4]}] The system must collect users' data in specific databases.
        \end{itemize}
        
    \item Allow a user to accept or refuse a request to access to personal data.
    \begin{itemize}
            \item [{[R6]}] Every time that a third party inserts a request for data relative a SSN or Fiscal Code, the system must ask authorizations to the user corresponding to those credentials.
            \item [{[R7]}] The system must provide a function to allow users to accept or refuse a request for personal data.
        \end{itemize}

    \item Allow third parties to register to the system.
        \begin{itemize}
            \item [{[D1]}] Users insert credentials that correspond to their identity.
            \item [{[D1]}] When a new registered user sends his/her credentials to the system, the message will be surely received.
            \item [{[R8]}] The system should provide a registration form to third parties.
            \item [{[R2]}] The system must guarantee that the credentials are unique.
        \end{itemize}
        
    \item Allow third parties to request an access to users' data.
    \begin{enumerate} [label*={.\arabic*}]
        \item [{[G6.1]}] Allow third parties to request access to data of some specific individuals by providing SSN or Fiscal Code.
            \begin{itemize}
                \item [{[R*]}] The system must provide a function to allow third parties to request the access to an individual's data. The form must require the filling of the SSN or Fiscal Code of the corresponding user.
            \end{itemize}
        \item [{[G6.2]}] Allow third parties to request access to anonymized data of group of people.
            \begin{itemize}
                \item [{[R*]}] The system must provide a function to allow third parties to request the access to data of a group of people. The form must offer some selection criteria such as geographical, time, health parameters, movement habits, ecc.
            \end{itemize}
    \end{enumerate}
    
    \item Send the demanded data to third parties whose request has been approved.
        \begin{itemize}
            \item [{[D3]}] The communication channel doesn't corrupt the data sent by the user's device to the system and vice versa.
            \item [{[R*]}] As soon as a request has been approved, the system must forward the most recent data to the third party applying for them.
            \item [{[R*]}] Data4Help must provide a function to third parties to download received data.
        \end{itemize}
        
        
    \item Accept request for data of group of people only if the system can guarantee the anonymity of the people.
        \begin{itemize}
            \item [{[D9]}] It’s sufficient that the number of people involved in a group query is greater than 1000 people to ensure the users’ privacy.
            \item [{[R*]}] The system accepts a request for anonymous data only if the group composing the data is formed by more than 1000 people.
        \end{itemize}
        
    \item Allow third parties to subscribe to new data and to receive them as soon as they are produced.
        \begin{itemize}
            \item [{[R3]}] The system must acquire real-time users' positions from the GPS installed on the user's device.
            \item [{[R5]}] The system must acquire real-time users' health parameters from the sensors installed on the user's device.
            \item [{[R*]}] The system must provide a function that allows to customize the requests for subscription to updated data. The request must include how long the permission is still valid.
            \item [{[R*]}] The system must provide a function to the corresponding user that allows him/her to accept or refuse the subscription request.
            %\item [{[R*]}] The system must provide a function to allow third parties to subscribe to updated users' data.
            \item [{[R*]}] The system must forward in real-time the most recent data to the third parties that subscribed to them.
        \end{itemize}
\end{enumerate}  
\noindent
AutomatedSOS:
\begin{enumerate} [resume, label={[G\arabic*]}]
    \item Allow a visitor to become registered user after providing credentials.
        \begin{itemize}
            \item [{[D1]}] Users insert credentials that correspond to their identity.
            \item [{[D2]}] When a new registered user sends his/her credentials to the system, the message will be surely received.
            \item [{[R1]}] The system should provide a registration form offering the following mandatory fields: name, surname, SSN or Fiscal Code.
            \item [{[R2]}] The system must guarantee that the credentials are unique.
        \end{itemize}
        
    \item Monitor the location of users through electronic devices.
        \begin{itemize}
            \item [{[D3]}] The communication channel doesn't corrupt the data sent by the user's device to the system and vice versa.
            \item [{[D4]}] The electronic device on which the system is installed is equipped with the GPS sensor.
            \item [{[D7]}] Position information provided by GPS is sufficiently accurate.
            \item [{[D11]}] Data  provided  by  Data4Help  API  are  surely  received  and  they  are  not corrupted.
            \item [{[R*]}] The system must acquire real-time users' position from the their device through the Data4Help API.
            \item [{[R*]}] The system saves the most recent user's position in a database.
        \end{itemize}
        
    \item Monitor the health status of users through electronic devices.
        \begin{itemize}
            \item [{[D3]}] The communication channel doesn't corrupt the data sent by the user's device to the system and vice versa.
            \item [{[D5]}] The electronic device on which the system is installed is equipped with the sensors related to the parameters tracked by Data4Help.
            \item [{[D6]}] The  system  retrieves  the  data  from  the  sensors  through  the  interfaces available on the electronic device.
            \item [{[D8]}] The sensors related to the health status collect the data with a reasonable precision.
            \item [{[D11]}] Data  provided  by  Data4Help  API  are  surely  received  and  they  are  not corrupted.
            \item [{[R*]}] The system must acquire real-time users' health parameters from their device through the Data4Help API.
            \item [{[R*]}] The system must elaborate users' data comparing each of them with a defined threshold. 
            \item [{[R*]}] Elaboration must be completed within 5 seconds from the instant the data are received.
        \end{itemize}
        
    \item Send to the location of the customer very quickly an ambulance when such parameters are below certain thresholds. 
        \begin{itemize}
            \item [{[D12]}] When an emergency request is sent to National Health Service, it surely receive it.
            \item [{[D13]}] When National Health Service receives an emergency request, at least an ambulance is available.
            \item [{[D14]}] When  parameters  are  below  certain  thresholds,  it  means  that  the  user actually needs first aid.
            \item [{[D15]}] Operations Center of the NHS is up 24/7.
            \item [{[D16]}] When Operations Center gather a request from AutomatedSOS, it sends at least an ambulance and at least one of them arrives to the location of the emergency.
            \item [{[D17]}] NHS provides an API that allows third parties to send emergency requests in the form of a instant message received in their platform.
            \item [{[R*]}] As soon as an anomaly in the parameters is detected,the system must organize the data in a human-readable request for first aid. The form for request must contain these mandatory fields: Name, Surname, Age, Gender, SSN or Fiscal Code, latest available position, list of the latest health parameters.
            \item [{[R*]}] AutomatedSOS must send a request for first aid to the Operations Center within 5 seconds from the moment that the emergency is detected.
            \item [{[R*]}] The system must send the request through the API provided by the NHS.
        \end{itemize}
\end{enumerate}


\section{Performance Requirements}

\section{Design Constraints}
\subsection{Standards compliance}
\subsection{Hardware limitations}
\subsection{Any other constraint}

\section{Software System Attributes}
\subsection{Reliability}
\subsection{Availability}
\subsection{Security}
\subsection{Maintainability}
\subsection{Portability}